---
title: "Explore Air Quality Measurements"
date: "2024-01-04"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
		      message=FALSE, 
		      warning=FALSE)

library(ggplot2)
library(datasets)
```

## Introduction

The task was to create a Shiny application and deploy it on Rstudio's servers.

My application can be found [here](https://mk-scp.shinyapps.io/Explore_Air_Quality/).

You can explore a dataset about air qualitiy measurements in New York with it.

The data is taken from "airquality" of the R-package "datasets".

## Functioning of the app

The R-Code to plot the data looks something like:

```{r simple_plot, echo = TRUE, fig.height=4}

ggplot(airquality, aes(x = Ozone, y = Wind)) + geom_point()
```

## Explore the data

- To explore the data and the relations between the variables you can choose the variables that are displayed.
- If you like you can draw a linear fit line by checking the relevant box.
- To quantify the relation the app calculates the correlation coefficient between the chosen variables. As for the fit you can show the correlation by checking a box.

```{r cor_coef, echo=TRUE}

cor_coef <- cor(airquality$Ozone, 
		airquality$Wind, 
		use = "complete.obs")
cor_coef <- round(cor_coef, 2)
cor_coef
```


## Resulting plot

By checking all boxes you get plots like:

```{r linear_fit, echo=FALSE}

ggplot(airquality, aes(x = Ozone, y = Wind)) +
	geom_point() +
	geom_smooth(method = "lm",
	      se = FALSE,
	      color = "red") +
	annotate(
		"label",
		x = 0.8 * max(airquality$Ozone, na.rm = TRUE),
		y = 0.95 * max(airquality$Wind, na.rm = TRUE),
		label = paste0("Correlation: ", round(cor(airquality$Ozone, airquality$Wind, use = "complete.obs"), 2)),
		size = 7
	)
```




